Checkpoint 4

### 2020-04-30 Checkpoint 4.Rmd
stuff

```{r}
### For predicting one case 
new_FL <- Finaldata%>% 
          filter(State=="FL") #filter the row of interest

set.seed(454)
pred_FL <- posterior_predict(
  model_100,
  newdata = new_FL)

pred_2 <- data.frame(y_new = pred_FL[-1])

>>>>

```{r}
### For predicting one case 
new_CA <- Finaldata%>% 
          filter(State=="CA") #filter the row of interest

set.seed(454)
pred_CA <- posterior_predict(
  model_100,
  newdata = new_CA)

pred_2 <- data.frame(y_new = pred_CA[-1])
